### 2023-02-05 README.Rmd
Change all `computing` to `computational` [no ci]
Update readme to reflect #1 [no ci]

@@

## Recreate the computing environment

The object can be used to recreate the computing environment via [Rocker](https://github.com/rocker-org/rocker).

@@

The logo of gran is a remix of [this](https://commons.wikimedia.org/wiki/File:Flag_of_the_Canary_Islands.svg) public domain image.

>>>>

Although this package can also be used to ensure the current R computational environment can be reconstructed by future researchers, this package gears towards reconstructing historical R computational environments which have not been completely declared. For the former purpose, packages such as [renv](https://github.com/rstudio/renv/), [groundhog](https://github.com/CredibilityLab/groundhog), [miniCRAN](https://github.com/andrie/miniCRAN), and [Require](https://github.com/PredictiveEcology/Require) should be used. One can think of gran as an archaeological tool.

To reconstruct a historical R computational environment, this package assumes only the availability of source packages on CRAN. The reconstruction procedures have been tested in several vintage versions of R.

@@

## Recreate the computational environment via Rocker

The object can be used to recreate the computational environment via [Rocker](https://github.com/rocker-org/rocker). Please note that the oldest R version one can get from Rocker is R 3.1.0.

@@

The logo of gran is a remix of [this](https://commons.wikimedia.org/wiki/File:Flag_of_the_Canary_Islands.svg) public domain image. The two dogs should be *Presa Canario*, the native dog breed on the islands of Gran Canaria and Tenerife.
